Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-15 ms.tex
Moved the purple banana to the panel that resembles a banana a bit better.

As is evident in Figure~\ref{fig:Mr20triangle}, $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
share a relatively narrow degeneracy as well. This degeneracy is largely induced by the 
measured number density of the sample. Increasing $\log (M_{\rm min})$ decreases galaxy 
number density, but this can be compensated by an increase in $\sigma_{\log M}$, which 
places galaxies in a fraction of the considerably more numerous halos with masses less 
than $M_{\rm min}$. The consequence is that $\log (M_{\rm min})$ and $\sigma_{\log M}$ are 
degenerate with each other such that most of the posterior probability lies in a narrow band 
along which $\log (M_{\rm min})$ and $\sigma_{\log M}$ are positively correlated. 
In the following plots, we exclude the parameter $\sigma_{\log M}$,  
in order to increase the clarity of the plots, because the viable range of $\sigma_{\log M}$ is 
determined by this simple degeneracy with $\log (M_{\rm min})$.

>>>>

Look for the purple banana\footnote{'Til they put us in the truck.} in the third panel from the left in the bottom row of 
Figure~\ref{fig:Mr20triangle}. This panel illustrates that the parameters 
$\log (M_{\rm min})$ and $\sigma_{\log M}$ share a relatively narrow degeneracy as well. 
This degeneracy is largely induced by the measured 
number density of the sample. Increasing $\log (M_{\rm min})$ decreases galaxy 
number density, but this can be compensated by an increase in $\sigma_{\log M}$, which 
places galaxies in a fraction of the considerably more numerous halos with masses less 
than $M_{\rm min}$. The consequence is that $\log (M_{\rm min})$ and $\sigma_{\log M}$ are 
degenerate with each other such that most of the posterior probability lies in a narrow band 
along which $\log (M_{\rm min})$ and $\sigma_{\log M}$ are positively correlated. 
In the following plots, we exclude the parameter $\sigma_{\log M}$,  
in order to increase the clarity of the plots, because the viable range of $\sigma_{\log M}$ is 
determined by this simple degeneracy with $\log (M_{\rm min})$.
